\documentclass[gradu,emptyfirstpagenumber]{tktltiki}
\usepackage{lmodern}
\usepackage{url}
\usepackage[dvips, bookmarks, colorlinks=false, pdftitle={Tuqqna - Connect Four
game}, pdfauthor={Sami Saada}, pdfsubject={Implementation Document}, pdfkeywords={PDF,
LaTeX, hyperlinks, hyperref}]{hyperref}

\begin{document}

\title{Tuqqna}
\author{Sami Saada}
\faculty{Faculty of Science}
\department{Department of Computer Science}
\level{Implementation Document}
\subject{Programming in Python}
\additionalinformation{Teacher is Harri Hämäläinen}
\numberofpagesinformation{\numberofpages\ pages}
\keywords{Python, Implementation document}

\maketitle

\begin{abstract}
This document tells implementation issues, about tests done, and the
instructions for the user of your program.
\end{abstract}

\mytableofcontents

\section{Implementation}

Tuqqna is Connect Four game. It has basic package - module hierarchy. Packages
are categorized. There is core package, which contains all core items, and cli
package, which contains all cli ui items. gui and ai packages are ready for
further developing.

You can play connect four with your friends with Tuqqna, that all what is needed
:)

\pagebreak

\section{Testing}

Testing has been done with unittest-module. Every core element is fully tested,
just because it is made by using TDD (Test Driven Development). Some UI elements
are also tested with unit tests, but not those which contains mainly curses
elements.

Tuqqna is also tested by human use.

\pagebreak

\section{Instructions}

User can play with Tuqqna just executing run.py -file.

User can run tests in Tuqqna just executing unittests.py -file.

Note: Do not resize terminal window during the game. Some elements will raise
error if game window is too small.

\pagebreak

\section{Python 2to3 conversion}

Every file in Tuqqna has been tested with $python -3$. The result is, that every
module will work out of box in python 3.

\lastpage
\appendices

\end{document}

\endinput
